Bayesian Networks for Assessing Environmental Sustainability in Australian Vineyards

### 2024-08-26 article.tex
initial mardi edits - pg 14

\section{Title}
A Bayesian Network Model based decision support tool for Environmental Sustainability in the Australian Winegrowing Industry.

@@

Environmental sustainability in the Australian winegrowing industry involves complex, interacting factors. To address this, we developed a Bayesian Network (BN) model, integrating data and expert input to summarise key factors, their relationships, and impacts on vineyard outcomes. The BN model was iteratively refined, involving variable selection, structure definition, and probability estimation, with expert input ensuring industry relevance and regional adaptability. A case study of the Coonawarra region highlighted regional differences while underscoring industry-wide concerns, such as agrochemical use. The BN model, accessible via an application, allows for continuous industry feedback and adaptation. This study underscores the potential of BNs as powerful tools for sustainability analysis in agriculture, offering valuable insights for sustainable vineyard management.

\section{Introduction}

The imperative for environmental sustainability in agriculture has intensified as the sector strives to balance productivity with ecological preservation~\cite{baianoOverviewSustainabilityWine2021,corboEnvironmentalSustainabilityPrograms2014}. This is especially true for Viticulture, the cultivation of grapevines for wine production, as it presents unique challenges and opportunities for sustainability, particularly due to its position as a luxury good amongst other agricultural industries~\cite{longbottomExploringLinksSustainability2018,ferraraLifeCycleAssessment2018}. This study investigates environmental sustainability practices in Australian winegrowing, using the application of Bayesian Networks (BNs). To create a rigorous and quantitative approach to understanding sustainable practices and the relationships between factors associated with these practices, a broad model of Australian winegrowing was created. This model was followed by a more specific case study looking at the Coonawarra winegrowing region.

@@

This research is guided by several fundamental inquiries aimed at enhancing our understanding of environmental sustainability in viticulture. A primary question is how key factors impacting environmental sustainability can be rigorously defined and quantified. Another focus delves into identifying the unique regional characteristics of different regions, using the Coonawarra winegrowing region to illustrate how the relative influence of factors might change regionally. Additionally, the study investigates how these factors interact with each other. The final question is, how the findings from these Bayesian Network models compare with existing literature on sustainability in viticulture, aiming to connect industry perceptions to academic knowledge.

An industry panel comprising experts in viticulture and environmental sustainability, was convened to guide the project. The panel acted as a catalyst in the early stages of the research to help explore the above questions. The panel input was supported by a comprehensive literature review, which established a foundational understanding of the current knowledge landscape and identified major concepts within sustainable winegrowing. To ensure a robust and comprehensive BN, a combination of qualitative and quantitative methods were employed in its creation via expert consultations and data analysis. The study thus aimed to produce findings that are not only theoretically sound but also practically relevant and applicable to the viticulture industry.

@@

In agriculture, the consideration of environment is critical to the success of the industry. The question of environmental sustainability has continued to grow in importance as the industry is affected by international market demands, disease pressures, natural disasters and social change \citep{wineaustraliaNationalVintageReport2022,wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,cassonMultidisciplinaryApproachAssess2022}. The question of sustainability requires the consideration of a multitude of factors, not only due to physical characteristics and differences between locations and habitats but also due to priorities driven by diverse perspectives including consumers, produces, the community, government and industry \citep{baianoOverviewSustainabilityWine2021,wayeCarbonFootprintsFood2008}. It is important to consider each factor with respect to these perspectives, and to be explicit in how they are defined \citep{santiago-brownSustainabilityAssessmentWineGrape2015}.

Collaboration between experts from different perspectives helps to reconcile opinions regarding different factors and their contribution to sustainable outcomes \citep{dichiaraCollaborativeApproachAchieving2024}. In Australia, all of the above groups mentioned are united in the priority to improve greenhouse gas emissions and resource inputs through approaches such as regulating chemicals, water use and fertilisers \citep{dumbrellComparingAustralianPublic2024}. While there is a general agreement on broader regulatory needs, the industry requirements vary greatly between different wine regions; due to climate, soil types and water resources \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012}.
% old comment
% KM: I Suggest expanding this (the paragraph below) - split into measurement, methods, etc - or leave this para out and absorb refs into the lit review. G, K and F seem quite relevant but this paragraph doesnt do them justice so expand or move.
% 
% Review further comments about this paragraph - its not a good piece of work but it is important to consider how impact and sustainability is or could be measured and interpretted. Perhaps go deeper like you did in your confirmation.
Methods for measuring sustainability comprise a wide variety that of approaches with the use of index systems being common. The use of index systems is beneficial in comparing sustainability performance across different industries or geographic regions. As \textcite{gehringerMappingSustainabilityMeasurement2024} notes, these systems provide a structured approach to evaluating sustainability by aggregating multiple indicators into a singular measure, facilitating easier interpretation and comparison.
Other approaches utilise the identification of key factors, and their measurements as a proxy to indicate impact to, or the health of, the environment \citep{floresWhatSustainabilityWine2018}. The measuring of sustainability through can help to manage risk and promote resilience for industries through identifying sustainable goals and key factors of interest that contribute to positive outcomes \citep{klemesAssessingMeasuringEnvironmental2015, beckerSustainabilityScienceManaging2024}. For instance, frameworks like MESMIS categorize sustainability measures into "descriptors" (guidelines), "indicators" (metrics for measuring changes), and "parameters" (limits for indicators) \citep{candido_sustainability_2015}. This structure allows for a more granular assessment of sustainability by linking broad guidelines to specific, measurable outcomes. By focusing on key indicators such as soil health, water usage, and biodiversity, the sustainability of wine production practices can be gauged with greater precision. These proxy measurements are crucial for understanding how specific actions or practices affect broader environmental outcomes, thereby enabling more targeted and effective sustainability efforts. Within this study we focus on measuring key factors and establishing how they interact, and ultimately effect the surrounding environment; the chosen method for this study is a Bayesian Network.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% End suggestion.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Literature Review}

The literature review was designed to access existing knowledge on environmental sustainability in viticulture with the aim of identifying key factors influencing sustainability and understanding their interactions.

These findings were combined with the information derived from the expert consultations to inform the BN construction and quantification. 
% Clarify that the review helped inform the strawman model and was only used as a comparison point afterwards.

@@

Once relevant articles were identified, data extraction was conducted to gather information on the key factors influencing environmental sustainability in viticulture, their interactions, and the methodologies used in studies that analysed any of the concepts listed by experts. The extracted data was then processed using Leximancer to identify common themes and concepts in the existing literature.

The expert panel comprising specialists in viticulture and environmental sustainability was engaged throughout the literature review process. The panel provided guidance on the selection of relevant articles, helped refine the inclusion criteria through their list of key factors.
% By conducting a thorough literature review, this study aimed to build a solid foundation of existing knowledge, identify gaps, and position the findings from the Bayesian Network models within the broader context of sustainability research in viticulture. This approach ensured that the study's results were not only robust and scientifically sound but also practically relevant and actionable for industry stakeholders.

@@

Due to Coonawarra's distinct characteristics and the expert panels' expertise, this region was the ideal case study for applying BNs. Located in South Australia's Limestone Coast zone, Coonawarra is characterised by its cooler Australian climate and the unique geology of the limestone coast, which provides an excellent foundation for viticulture. The Coonawarra winegrowing region is renowned for its exceptional wine quality, particularly its Cabernet Sauvignon \cite{hallidayAustralianWineEncyclopedia2009}. Due to the region's distinct characteristics and the expert panels' expertise, this region was the ideal case study for applying Bayesian Networks using the expert panels overarching ideas around environmental sustainability practices to specific regional factors.

@@

The key factors identified by the industry panel and their agreed definitions are shown in Table \ref{tab:definitions}. By utilising these definitions, each factor's contribution to environmental sustainability were quantified and assessed by the industry panel. The quantification of each factor allowed for a systematic assessment of their impacts. For example, "Water Use" was quantified as "High" or "Low," enabling a straightforward assessment of its environmental impact. Similarly, other factors were defined and quantified to ensure their contributions to sustainability were measurable; with each being of the two general categories ideal and not ideal (low and high respectively for water use).

% How can these key factors be rigorously defined so that they are quantifiable contributions to environmental sustainability?
% Purpose: Develop the factors into well-defined and measurable impacts on environmental sustainability.
% Results: Use the agreed upon definitions to fully realise factors and their impact.
% 
% Please add the following required packages to your document preamble:
% \usepackage{booktabs} TODO: check the BN definitions align properly.
%

@@

    \textbf{Weather Conditions} & A vineyard’s regional climatic conditions. & \textbf{Ideal} & Not Ideal \\

@@

By applying these definitions, the study effectively translated the qualitative aspects of environmental sustainability into usable metrics. This approach not only facilitated a comprehensive analysis of the factors but also identified their specific relationships. The use of these definitions enabled each of the factors' impacts to be linked and reviewed, demonstrating their importance in achieving environmental sustainability; allowing each factor's contribution to be clearly understood and relationships explicitly defined. This was key within the construction of the BN, were the industry panel could easily refer to the specifics of each definition and thus how it might relate to other factors.

\subsection{Bayesian Network Structure for Environmental Sustainability in Australian Winegrowing}

@@

    % What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?
    %     Purpose: Identify the most influential variables directly affecting environmental sustainability and those that are perceived to directly impact environmental sustainability.
    %     Results: Review the most influential factors and what they are related too. Compare this to the data in SWA.

@@

% The BN provided a comprehensive overview of how factors defined by the industry panel, would interact. Showing not only direct relationships but also how changes in one factor can propagate through the network to affect others. This understanding is crucial for developing targeted interventions and policies aimed at improving sustainability in the winegrowing industry. This network illustrates the complexity of interactions that define environmental sustainability in Australian winegrowing. Furthermore, the extent of relationships helps to intrinsically show the importance of variables such as water; which is prolific in how it is interconnected with other vineyard aspects.

Figure~\ref{fig:generalBN}, illustrates the intricate relationships between various vineyard factors and their impact on environmental sustainability in the Australian winegrowing industry. The BN structure highlights the critical role of water, disease/pest management, and climate, which are depicted as central nodes with numerous connections to other variables. These connections underscore the importance of these factors as key drivers of environmental impact, influencing a wide number of other nodes within the network.

@@

As part of this study, a comprehensive literature review was conducted to assess the current state of research on environmental sustainability in the winegrowing industry and as part of the BNs validation. The review included a total of 1321 articles, selected based on key words and publication dates outlined in the prior selection criteria (see \ref{query}). The articles span a range of topics, including sustainability metrics, operational practices, and the influence of regulatory frameworks on environmental outcomes.

The number of articles that contained key terms is outlined in Table \ref{tab:lexi}. The bibliometric analysis using Leximancer revealed key concepts and their relevance to environmental sustainability in the Australian winegrowing industry. The most prominent concept was water (see Table \ref{tab:lexi}). The critical importance of other variables is indicated by their comparative appearance in articles relative to water (making water 100\%).This review provided a foundation for comparing academic perspectives with industry practices, allowing for a nuanced analysis of how well the literature aligns with challenges and solutions outlined by the expert panel.

    % What are the factors of environmental sustainability in the Australian winegrowing industry?
    %     Purpose: Explore and understand the both the literature and industry perspectives on this.
    %     Results Literature review. Industry list of factors. Mind Map? Leximancer network.
    %     - Use the same words as the definitions in the search to show the parralels and differences.

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[h]\label{tab:lexi}
    \caption{Table \ref{tab:lexi} Table \ref{tab}: Key Concepts Identified in the Bibliometric Analysis of Environmental Sustainability in the Australian Winegrowing Industry.}
    \begin{tabular}{@{}lrr@{}}
    \toprule
    \textbf{Concept} & \multicolumn{1}{l}{\textbf{Count}} & \multicolumn{1}{l}{\textbf{Relevance_percentage}} \\ \midrule
    water & 1321 & 100 \\
    change & 817 & 62 \\
    climate & 789 & 60 \\
    disease & 646 & 49 \\
    change & 569 & 43 \\
    grapevine & 565 & 43 \\
    viticulture & 565 & 43 \\
    soil & 450 & 34 \\
    plant & 425 & 32 \\
    different & 300 & 23 \\ \bottomrule
    \end{tabular}
    \end{table}

@@

A key difference between the concepts from the literature search and the BN based on the industry panel was the rarity in how secondary and tertiary drivers of industry such as fuel or electricity use, were connected to primary sustainable concerns such as disease (even though disease was quite prominent in both). 
% With these concepts being related to the operations in fields as a result of changing practices or implementing different pest controls. Together these outputs provide a comprehensive overview of the key factors affecting environmental sustainability in the Australian winegrowing industry, offering valuable insights into areas of focus and potential improvement. This analysis underscores the multifaceted nature of sustainability, highlighting both the primary concerns and the interconnected secondary factors that must be managed on the ground.

@@

Two distinct BNs were constructed for the Coonawarra region, each reflecting alternative points of view taken by experts. The models diverged in their structural representations with a differing emphasis on specific causal relationships. One BN  (see Figure \ref{fig:marcel} explicitly incorporated connections between soil degradation and tractor passes, as well as between weather conditions and agrochemical scores. The other BN, while structurally similar, did not include these connections. The use of two separately scored BNs with differing structure ensured that the BNs captured the diversity of expert views regarding the primary drivers of environmental outcomes in the region.

Identified key factors impacting environmental sustainability were examined with regard to Coonawarra. By comparing the generic Bayesian Network (Figure \ref{fig:b}) model to the Coonawarra-specific model (Figure \ref{fig:robyn} and Figure \ref{fig:marcel}), we identified regional characteristics that influence these variations. In this case study, we altered the general Australian BN to model and analyse the complex interactions between various environmental factors affecting wine production in Coonawarra. By incorporating industry-specific data and expert knowledge, the BN framework allowed us to quantify the impacts of key variables such as water use, agrochemical application, soil health, and climate conditions to each other. This approach not only aids in understanding the current sustainability status of the region but also helps in identifying potential areas for improvement and implementing effective management strategies. The resultant two models represent the final consensus, reflecting the diverse perspectives and occasionally differing viewpoints among the experts, necessitating the development of two distinct but complementary models.

Key factors impacting environmental sustainability in Coonawarra were examined by developing region-specific BNs, Figure \ref{fig:robyn} and Figure \ref{fig:marcel} were based on the generic structural model illustrated in Figure \ref{fig}. The general model was adapted to reflect the unique regional characteristics of Coonawarra, resulting in some structural differences between the region specific models as well as the original generic model. These adaptations allowed us to review the interactions between key environmental factors such as water use, agrochemical application, soil health, and climate conditions. The importance of these variables is highlighted through their relative weightings, as determined by expert input, offering a nuanced understanding of sustainability in the Coonawarra wineregion.The two case study BNs are almost identical in their significant factors and interactions. Both emphasize the importance of water quality, pest and disease management, and climate conditions. The primary difference is the sensitivity to tractor passes, water quality, water scarcity, and soil degradation management, with Figure \ref{fig:robyn} showing higher sensitivity to these factors.

@@

    % How do changes in key factors under various environmental and regulatory scenarios influence the overall environmental impact in Coonawarra?
    %     Purpose: Assess different factors overall influence to environmental sustainability given the definitions used.
    %     Results: Use the CPT values to assess the significant contribution of different variables on the BN and how that effects environmental sustainability.

\begin{figure}[h!]
    \centering
    \includegraphics[width=\linewidth]{robyn}
    \caption{Coonawarra-specific Bayesian Network illustrating key factors impacting environmental sustainability, with nodes coloured by sensitivity to environmental impact.}\label{fig:robyn}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=\linewidth]{marcel}
    \caption{Coonawarra-specific Bayesian Network illustrating key factors impacting environmental sustainability, with nodes coloured by sensitivity to environmental impact.}\label{fig:marcel}
\end{figure}

@@

The primary difference in interactions between the two BNs (see Figure~\ref{fig:robyn} and~\ref{fig:marcel}) lies in vineyard floor management, seasonal conditions and tractor passes. In Figure \ref{fig:marcel}, greater tractor passes were used purposefully to manage the vineyard floor; as opposed to Figure \ref{fig:robyn} where vineyard floor was managed as a consequence of tractor passes, leveraging opportunities when the tractor was used. This distinction highlighted how operational decisions can vary based on regional practices and priorities. A point was also raised that scale can cause a further driving factor, where tractor passes may be greatly increased as an expense on larger plots of land. However, this issue as well as directly attributing measurable cause to granular specifics such as composting, soil depth and clay content cannot be fully addressed without site or paddock specific knowledge.

As a factor, water emerged as the most interconnected variable for both BNs, with edges connecting it to almost everything either directly or indirectly, illustrating its fundamental role in agriculture. Weather conditions also play a significant role, influencing water availability, quality and disease/pest pressures. Within both of the models, the most significant factors impacting environmental sustainability are water quality, pest and disease management, market pressures, agrochemical use, and climate/weather conditions. These factors were identified as having the highest sensitivity to environmental impact, indicating their crucial roles in the sustainability of the region.

@@

%  Aside from the role of tractor passes, there are no major differences between the two BNs. The similarity in significant factors and their interactions underscores the robustness of the BN approach in capturing the critical elements of environmental sustainability in winegrowing.

@@

% Question: What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?

>>>>

\section{Title}
A Bayesian Network Model based decision support tool for sustainability in the Australian Winegrowing Industry.

@@

Sustainability in the Australian winegrowing industry involves complex, interacting factors. To address this, we developed a Bayesian Network (BN) model, integrating data and expert input to summarise key factors, their relationships, and impacts on vineyard outcomes. The BN model was iteratively refined, involving variable selection, structure definition, and probability estimation, with expert input ensuring industry relevance and regional adaptability. A case study of the Coonawarra region highlighted regional differences while underscoring industry-wide concerns, such as agrochemical use. The BN model, accessible via an application, allows for continuous industry feedback and adaptation. This study underscores the potential of BNs as powerful tools for sustainability analysis in agriculture, offering valuable insights for sustainable vineyard management.

\section{Introduction}
% TODO: introduce the concept of sustainability and define it! Especially within the context of this study!! 
The imperative for sustainability in agriculture has intensified as the sector strives to balance productivity with ecological preservation~\cite{baianoOverviewSustainabilityWine2021,corboEnvironmentalSustainabilityPrograms2014}. This is especially true for viticulture, the cultivation of grapevines for wine production, as it presents unique challenges and opportunities for sustainability, particularly due to its position as a luxury good amongst other agricultural industries~\cite{longbottomExploringLinksSustainability2018,ferraraLifeCycleAssessment2018}. This study investigates sustainability practices in Australian winegrowing, using the application of Bayesian Networks (BNs). To create a rigorous and quantitative approach to understanding sustainable practices and the relationships between factors associated with these practices, a broad model of Australian winegrowing was created. This model was followed by a more specific case study looking at the Coonawarra winegrowing region.

@@

This research is guided by several fundamental inquiries aimed at enhancing our understanding of sustainability in viticulture. A primary question is how key factors impacting sustainability can be rigorously defined and quantified. Another focus delves into identifying the unique regional characteristics of different regions, using the Coonawarra winegrowing region to illustrate how the relative influence of factors might change regionally. Additionally, the study investigates how these factors interact with each other. The final question is, how the findings from these Bayesian Network models compare with existing literature on sustainability in viticulture, aiming to connect industry perceptions to academic knowledge.

An industry panel comprising experts in viticulture and sustainability, was convened to guide the project. The panel acted as a catalyst in the early stages of the research to help explore the above questions. The panel input was supported by a comprehensive literature review, which established a foundational understanding of the current knowledge landscape and identified major concepts within sustainable winegrowing. To ensure a robust and comprehensive BN, a combination of qualitative and quantitative methods were employed in its creation via expert consultations and data analysis. The study thus aimed to produce findings that are not only theoretically sound but also practically relevant and applicable to the viticulture industry.

@@

In agriculture, the consideration of environment is critical to the success of the industry. The question of sustainability has continued to grow in importance as the industry is affected by international market demands, disease pressures, natural disasters and social change \citep{wineaustraliaNationalVintageReport2022,wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,cassonMultidisciplinaryApproachAssess2022}. The question of sustainability requires the consideration of a multitude of factors, not only due to physical characteristics and differences between locations and habitats but also due to priorities driven by diverse perspectives including consumers, produces, the community, government and industry \citep{baianoOverviewSustainabilityWine2021,wayeCarbonFootprintsFood2008}. It is important to consider each factor with respect to these perspectives, and to be explicit in how they are defined \citep{santiago-brownSustainabilityAssessmentWineGrape2015}.

Collaboration between experts from different perspectives helps to reconcile opinions regarding different factors and their contribution to sustainable outcomes \citep{dichiaraCollaborativeApproachAchieving2024}. In Australia, all of the above groups mentioned are united in the priority to reduce greenhouse gas emissions and resource use through approaches such as regulating chemicals, water use and fertilisers \citep{dumbrellComparingAustralianPublic2024}. While there is a general agreement on broader regulatory needs, the industry requirements vary greatly between different wine regions; due to climate, soil types and water resources \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012}.
% old comment
% KM: I Suggest expanding this (the paragraph below) - split into measurement, methods, etc - or leave this para out and absorb refs into the lit review. G, K and F seem quite relevant but this paragraph doesnt do them justice so expand or move.
% 
% Review further comments about this paragraph - its not a good piece of work but it is important to consider how impact and sustainability is or could be measured and interpretted. Perhaps go deeper like you did in your confirmation.
Methods for measuring sustainability comprise a wide variety that of approaches with the use of index systems being common. The use of index systems is beneficial in comparing sustainability performance across different industries or geographic regions. As \textcite{gehringerMappingSustainabilityMeasurement2024} notes, these systems provide a structured approach to evaluating sustainability by aggregating multiple indicators into a singular measure, facilitating easier interpretation and comparison.
Other approaches utilise the identification of key factors, and their measurements as a proxy to indicate impact to, or the health of, the environment \citep{floresWhatSustainabilityWine2018}. The measuring of sustainability through can help to manage risk and promote resilience for industries through identifying sustainable goals and key factors of interest that contribute to positive outcomes \citep{klemesAssessingMeasuringEnvironmental2015, beckerSustainabilityScienceManaging2024}. For instance, frameworks like MESMIS categorize sustainability measures into "descriptors" (guidelines), "indicators" (metrics for measuring changes), and "parameters" (limits for indicators) \citep{candido_sustainability_2015}. This structure allows for a more granular assessment of sustainability by linking broad guidelines to specific, measurable outcomes. By focusing on key indicators such as soil health, water usage, and biodiversity, the sustainability of wine production practices can be gauged with greater precision. These proxy measurements are crucial for understanding how specific actions or practices affect broader environmental outcomes, thereby enabling more targeted and effective sustainability efforts. Within this study we focus on measuring key factors and establishing how they interact, and ultimately effect the surrounding environment; the chosen method for this study is a Bayesian Network.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% End suggestion.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Literature Review}

The literature review was designed to access existing knowledge on sustainability in viticulture with the aim of identifying key factors influencing sustainability and understanding their interactions.

These findings were combined with the information derived from the expert consultations to inform the BN construction and quantification. 
% TODO: Clarify that the review helped inform the strawman model and was only used as a comparison point afterwards.

@@

Once relevant articles were identified, data extraction was conducted to gather information on the key factors influencing sustainability in viticulture, their interactions, and the methodologies used in studies that analysed any of the concepts listed by experts. The extracted data was then processed using Leximancer to identify common themes and concepts in the existing literature.

The expert panel comprising specialists in viticulture and sustainability was engaged throughout the literature review process. The panel provided guidance on the selection of relevant articles, helped refine the inclusion criteria through their list of key factors.
% By conducting a thorough literature review, this study aimed to build a solid foundation of existing knowledge, identify gaps, and position the findings from the Bayesian Network models within the broader context of sustainability research in viticulture. This approach ensured that the study's results were not only robust and scientifically sound but also practically relevant and actionable for industry stakeholders.

@@

Due to Coonawarra's distinct characteristics and the expert panels' expertise, this region was the ideal case study for applying BNs. Located in South Australia's Limestone Coast zone, Coonawarra is distinguished by its cooler climate and the unique soils shaped by the region's distinctive geology. This combination provides an exceptional foundation for viticulture, making Coonawarra a renowned wine-producing area. The Coonawarra winegrowing region is renowned for its exceptional wine quality, particularly its Cabernet Sauvignon \cite{hallidayAustralianWineEncyclopedia2009}. Due to the region's distinct characteristics and the expert panels' expertise, this region was the ideal case study for applying Bayesian Networks using the expert panels overarching ideas around sustainability practices to specific regional factors.

@@

The key factors identified by the industry panel and their agreed definitions are shown in Table \ref{tab:definitions}. By utilising these definitions, each factor's contribution to sustainability were quantified and assessed by the industry panel. The quantification of each factor allowed for a systematic assessment of their impacts. For example, "Water Use" was quantified as "High" or "Low," enabling a straightforward assessment of its environmental impact. Similarly, other factors were defined and quantified to ensure their contributions to sustainability were measurable; with each being of the two general categories ideal and not ideal (low and high respectively for water use).

% How can these key factors be rigorously defined so that they are quantifiable contributions to sustainability?
% Purpose: Develop the factors into well-defined and measurable impacts on sustainability.
% Results: Use the agreed upon definitions to fully realise factors and their impact.
% 
% Please add the following required packages to your document preamble:
% \usepackage{booktabs} TODO: check the BN definitions align properly.
%

@@

    \textbf{Climate Conditions} & A vineyard’s regional climatic conditions. & \textbf{Ideal} & Not Ideal \\

@@

By applying these definitions, the study effectively translated the qualitative aspects of sustainability into usable metrics. This approach not only facilitated a comprehensive analysis of the factors but also identified their specific relationships. The use of these definitions enabled each of the factors' impacts to be linked and reviewed, demonstrating their importance in achieving sustainability; allowing each factor's contribution to be clearly understood and relationships explicitly defined. This was key within the construction of the BN, were the industry panel could easily refer to the specifics of each definition and thus how it might relate to other factors.

\subsection{Bayesian Network Structure for sustainability in Australian Winegrowing}

@@

    % What are the primary factors that significantly impact sustainability in the Australian winegrowing industry?
    %     Purpose: Identify the most influential variables directly affecting sustainability and those that are perceived to directly impact sustainability.
    %     Results: Review the most influential factors and what they are related too. Compare this to the data in SWA.

@@

% The BN provided a comprehensive overview of how factors defined by the industry panel, would interact. Showing not only direct relationships but also how changes in one factor can propagate through the network to affect others. This understanding is crucial for developing targeted interventions and policies aimed at improving sustainability in the winegrowing industry. This network illustrates the complexity of interactions that determine sustainability in Australian winegrowing. Furthermore, the extent of relationships helps to intrinsically show the importance of variables such as water; which is prolific in how it is interconnected with other vineyard aspects.

Figure~\ref{fig:generalBN}, illustrates the intricate relationships between various vineyard factors and their impact on sustainability in the Australian winegrowing industry. The BN structure highlights the critical role of water, disease/pest management, and climate, which are depicted as central nodes with numerous connections to other variables. These connections underscore the importance of these factors as key drivers of environmental impact, influencing a wide number of other nodes within the network.

@@

As part of this study, a comprehensive literature review was conducted to assess the current state of research on sustainability in the winegrowing industry and as part of the BNs validation. The review included a total of 1321 articles, selected based on key words and publication dates outlined in the prior selection criteria (see \ref{query}). The articles span a range of topics, including sustainability metrics, operational practices, and the influence of regulatory frameworks on environmental outcomes.

The number of articles that contained key terms is outlined in Table \ref{tab:lexi}. The bibliometric analysis using Leximancer revealed key concepts and their relevance to sustainability in the Australian winegrowing industry. The most prominent concept was water (see Table \ref{tab:lexi}). The critical importance of other variables is indicated by their comparative frequncy in articles relative to water (making water 100\%).This review provided a foundation for comparing academic perspectives with industry practices, allowing for a nuanced analysis of how well the literature aligns with challenges and solutions outlined by the expert panel.

    % What are the factors of sustainability in the Australian winegrowing industry?
    %     Purpose: Explore and understand the both the literature and industry perspectives on this.
    %     Results Literature review. Industry list of factors. Mind Map? Leximancer network.
    %     - Use the same words as the definitions in the search to show the parralels and differences.

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[h]\label{tab:lexi}
    \caption{Table \ref{tab:lexi} Table \ref{tab}: Key Concepts Identified in the Bibliometric Analysis of sustainability in the Australian Winegrowing Industry.}
    \begin{tabular}{@{}lrr@{}}
    \toprule
    \textbf{Concept} & \multicolumn{1}{l}{\textbf{Count}} & \multicolumn{1}{l}{\textbf{Relevance_percentage}} \\ \midrule
    water & 1321 & 100 \\
    change & 817 & 62 \\
    climate & 789 & 60 \\
    disease & 646 & 49 \\
    change & 569 & 43 \\ %TODO: One of these should be something other than change!!! THey both cant be!!
    grapevine & 565 & 43 \\
    viticulture & 565 & 43 \\
    soil & 450 & 34 \\
    plant & 425 & 32 \\
    different & 300 & 23 \\ \bottomrule
    \end{tabular}
    \end{table}

@@

A key difference between the concepts from the literature search and the BN based on the industry panel was the rarity in how secondary and tertiary drivers of industry such as fuel or electricity use, were connected to primary sustainability concerns such as disease (even though disease was quite prominent in both).\
% TODO: THis is a key point can you explore this a bit more by telling us the practical impact and implications? DOes it mean the prev research has focussed on the wrong areas and what does it mean we need to do? More in a particular area?
% TODO: Note the discussion with Mardi surrounding causality. And discuss further the differences later on about how the models both result in the same significant concerns for sustainability even though they are different models and even though some of the causality is shifted.
%  What does it mean? That some operational decisions are paramount to sustainability in an environmental context.
% That different approaches can have different causal relationships - i.e spraying for prevention and spraying in response to disease.
% That management strategies might change the emphasis of certain affects, or change the ability to control different minor outcomes but some concerns are more important and require direct attention such as disease pressures.
% It is incredibly important that we can acknowledge that some of these relationships can exist as dual casualities or bi-directionally, which brings into question models that cannot take this into account. Or take into account the difference in management strategies and how that does or does not change environmental concerns.

% With these concepts being related to the operations in fields as a result of changing practices or implementing different pest controls. Together these outputs provide a comprehensive overview of the key factors affecting sustainability in the Australian winegrowing industry, offering valuable insights into areas of focus and potential improvement. This analysis underscores the multifaceted nature of sustainability, highlighting both the primary concerns and the interconnected secondary factors that must be managed on the ground.
% TODO: ML: I don't understand how these words were selected. Are they concepts or just frequently used words. Are they al relevant? May need some explanation. - in reference to the Leximancer diagram.

@@

Two distinct BNs were constructed for the Coonawarra region, each reflecting alternative points of view taken by experts. The models diverged in their structural representations with a differing emphasis on specific causal relationships. One BN  (see Figure \ref{fig:marcel} explicitly incorporated connections between soil degradation and tractor passes, as well as between climate conditions and agrochemical scores. The other BN, while structurally similar, did not include these connections. The use of two separately scored BNs with differing structure ensured that the BNs captured the diversity of expert views regarding the primary drivers of environmental outcomes in the region.

Identified key factors impacting sustainability were examined with regard to Coonawarra. By comparing the generic Bayesian Network (Figure \ref{fig:b}) model to the Coonawarra-specific model (Figure \ref{fig:robyn} and Figure \ref{fig:marcel}), we identified regional characteristics that influence these variations. In this case study, we altered the general Australian BN to model and analyse the complex interactions between various environmental factors affecting wine production in Coonawarra. By incorporating industry-specific data and expert knowledge, the BN framework allowed us to quantify the impacts of key variables such as water use, agrochemical application, soil health, and climate conditions to each other. This approach not only aids in understanding the current sustainability status of the region but also helps in identifying potential areas for improvement and implementing effective management strategies. The resultant two models represent the final consensus, reflecting the diverse perspectives and occasionally differing viewpoints among the experts, necessitating the development of two distinct but complementary models.

Key factors impacting sustainability in Coonawarra were examined by developing region-specific BNs, Figure \ref{fig:robyn} and Figure \ref{fig:marcel} were based on the generic structural model illustrated in Figure \ref{fig}. The general model was adapted to reflect the unique regional characteristics of Coonawarra, resulting in some structural differences between the region specific models as well as the original generic model. These adaptations allowed us to review the interactions between key environmental factors such as water use, agrochemical application, soil health, and climate conditions. The importance of these variables is highlighted through their relative weightings, as determined by expert input, offering a nuanced understanding of sustainability in the Coonawarra wineregion.The two case study BNs are almost identical in their significant factors and interactions. Both emphasize the importance of water quality, pest and disease management, and climate conditions. The primary difference is the sensitivity to tractor passes, water quality, water scarcity, and soil degradation management, with Figure \ref{fig:robyn} showing higher sensitivity to these factors.

@@

    % How do changes in key factors under various environmental and regulatory scenarios influence the overall environmental impact in Coonawarra?
    %     Purpose: Assess different factors overall influence to sustainability given the definitions used.
    %     Results: Use the CPT values to assess the significant contribution of different variables on the BN and how that effects sustainability.

\begin{figure}[h!]
    \centering
    \includegraphics[width=\linewidth]{robyn}
    \caption{Coonawarra-specific Bayesian Network illustrating key factors impacting sustainability, with nodes coloured by sensitivity to environmental impact.}\label{fig:robyn}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=\linewidth]{marcel}
    \caption{Coonawarra-specific Bayesian Network illustrating key factors impacting sustainability, with nodes coloured by sensitivity to environmental impact.}\label{fig:marcel}
\end{figure}

@@

The primary difference in interactions between the two BNs (see Figure~\ref{fig:robyn} and~\ref{fig:marcel}) lies in vineyard floor management, seasonal conditions and tractor passes. In Figure \ref{fig:marcel}, a higher number of tractor passes were used purposefully to manage the vineyard floor; as opposed to Figure \ref{fig:robyn} where vineyard floor was managed as a consequence of tractor passes, leveraging opportunities when the tractor was used. 
% TODO: the prior sentance is not likely to be understood by a more general audience. also why?
This distinction highlighted how operational decisions can vary based on regional practices and priorities. A point was also raised that scale can cause a further driving factor, where tractor passes may be greatly increased as an expense on larger plots of land. However, this issue as well as directly attributing measurable cause to granular specifics such as composting, soil depth and clay content cannot be fully addressed without site or paddock specific knowledge.

As a factor, water emerged as the most interconnected variable for both BNs, with edges connecting it to almost everything either directly or indirectly, illustrating its fundamental role in agriculture. Climate conditions also play a significant role, influencing water availability, quality and disease/pest pressures. Within both of the models, the most significant factors impacting sustainability are water quality, pest and disease management, market pressures, agrochemical use, and climate conditions. These factors were identified as having the highest sensitivity to environmental impact, indicating their crucial roles in the sustainability of the region.

@@

%  Aside from the role of tractor passes, there are no major differences between the two BNs. The similarity in significant factors and their interactions underscores the robustness of the BN approach in capturing the critical elements of sustainability in winegrowing.

@@

% Question: What are the primary factors that significantly impact sustainability in the Australian winegrowing industry?
